Universal Anonymous Signatures

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Updates in MPS construction.

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^1,\feval^{\yeval^1},
\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
any open function. Concretely, by restricting to a system with one issuer and
one opener, one credential per user, one attribute per credential (the user
secret key)% , $\fissue^1$ issuance functions, and
% \feval functions that only use the $\yeval^1$ output -- which we denote with
% $\feval^{\yeval^1}$
.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
\CUASGen with only one issuer and opener, one credential per user, and one
attribute per credential (the user secret key), implements an MPS scheme where
$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
user, and one attribute per credential, can be done as in
\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
parameterized with a value $j$, which essentially is the result of applying $F$
to the message and signer identity, and is not leaked to the opener nor any
other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
encrypted with a single-use key pair, and is an input of \yinsp.

>>>>

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I,L},\feval^{\yeval^1},
\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
any open function. Concretely, by restricting to a system with one issuer and
one opener, one credential per user, one attribute per credential (the user
secret key)% , $\fissue^1$ issuance functions, and
% \feval functions that only use the $\yeval^1$ output -- which we denote with
% $\feval^{\yeval^1}$
.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I,L},\feval^{\yeval^1},
\finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one
credential per user, and one attribute per credential (the user secret key),
implements an MPS scheme where $F=\feval^{\yeval^1}$ and $G=\finsp^\ast$.
With these functions, the construction is essentially as in
\secref{ssec:related-models-gs}.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
is an input of \yinsp.
